
<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{A package to produce Metafeature plots}
-->


SNPVizualTools Basics
====================================================================


### Loading SNPVizualTools package and dependencies

```{r libraryLoad}
suppressMessages(library(SNPVizualTools))
```


### How to generate a basic vizualisations

First define the chromosome you want to study (current_chr) and get the 
available data (my.data) for this chromosome:
```{r, eval=FALSE}
current_chr <- "chr12"
my.data <- loadChrData()
```

The define the area to vizualise: 
```{r, eval=FALSE}
current_range <- setStudyRange(27950000, 28735000)
```

The loaded data will be screened and the found interactions will transform into
Genomic Ranges (my.ranges):
```{r, eval=FALSE}
my.ranges <- getDataOverview()
```

The **my.ranges** variable is a list containing three elements: **arch**, 
**circos** and **lncrna**.
Each element is designed for a type of visual representation:

- **arch** will be used with the function `drawArchs`

- **circos** will be used with the function `drawCircos`

- **lncrna** will be used with the function `drawLncrnas`



#### Draw Archs
You can draw the HiC and ChIA-PET arches with functions `drawArchs` to generate
ggplot arches and `tracks` to print them. By default, this function uses 
**my.ranges** data.

```{r, eval=FALSE}
arches_track <- drawArchs()
tracks(arches_track) + xlim(current_range)
```

If you want to highlight some regions, you can provide a list of highlight 
regions. A highlight region will be generated throught the `setHighLight` 
function. This function needs a start and a stop to define the region to 
highlight and a method defining the way to highlight this specific zone (by 
increasing its alpha or changing its color):

```{r, eval=FALSE}
specific_range1 <- setHighLight(28111017,28127138,"alpha")
specific_range2 <- setHighLight(28284682,28287682,"alpha")
specific_range3 <- setHighLight(28284682,28287682,"color")

arches_track <- drawArchs(highlight_range_list = list(specific_range1,specific_range2, specific_range3))
tracks(arches_track) + xlim(current_range)
```


By default, all the replicates of an experiment are processed individually.
After generated the **my.ranges** variable, you can manually merged some lines :

```{r, eval=FALSE}
k562_chiapet <- mergeRanges(c(my.ranges$arch$sgp_k562_lane13, my.ranges$arch$sgp_k562_lane24), label = "K562 ChiA-PET SGP")
```

You can vizualise the resulting figure like that :
```{r, eval=FALSE}
specific_range1 <- setHighLight(28111017,28127138,"alpha")

custom_track <- drawArchs(ranges_list = k562_chiapet, highlight_range_list = list(specific_range1))
tracks(custom_track) + xlim(current_range)
```

To re-organize (select, order and/or merge) several the ranges you can use the 
powerful function `organizeRanges`. You have to provide a vector with the index 
of the tracks if you have already generated a first figure with all the 
informative tracks (track_index) OR a vector with the index of the range how 
they appear in **my.range** (range_index)  and a vector with the labels of 
tracks if you want to change them.
The following syntax indicate you to merge two or more tracks : `1;4`. 

Here is an example :
```{r, eval=FALSE}
index = c("1;2;4","3;5","9","7")
labels =  c("Chiapet 1", "Chiapet 2", "HiC 2", NA)
custom_ranges <- organizeRanges(track_index = index, labels = labels)

specific_range1 <- setHighLight(28111017,28127138,"alpha")
custom_track <- drawArchs(ranges_list = custom_ranges, highlight_range_list = list(specific_range1))
tracks(custom_track) + xlim(current_range)
```

The resulting track is the fusion of track 1, 2 and 4 renamed "Chiapet 1", 
following by of track 3 and 5 renamed "Chiapet 2", the nineth track renamed 
"HiC 2" and then the seventh track with its original label.




